---
output:
  html_document: default
  pdf_document: default
---
---
title: "Brownlows Bets"
author: "Put your name here!"
date: "put the date here"
output: html_document: default
 ---

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 1137 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 1137 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->


#Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting!-->
```{r}
require(tigerstats)
ansarray <- numeric()
for (j in 1:100){
brownProfit = 0
bdays <- (1:365)
for (i in 1:1137){
students <- sample(bdays, 35, replace = TRUE)
xx <- duplicated(students)
WinLose <- sum(xx)
if (WinLose >= 1) brownProfit = brownProfit + 1 else brownProfit = brownProfit - 2
}
ansarray[j]=brownProfit
}
hist(ansarray)
favstats(ansarray)
```


That loop of total tests is repeated 100 times with profits assigned to an array called "ansarray." We found that the mean profit was $`r round(mean(ansarray))`. In other words, after making his birthday wager 1137 times, and then repeating that 100 more times, we estimate that the profit Professor Brownlow made was $`r round(mean(ansarray))`.

# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows-->
We now want to construct a 95% confidence interval. In order to find this range, we will calculate two standard deviations below and above the mean.   
```{r}
est <- mean(ansarray)
sd <- sd(ansarray)
conf <- c(est - 2*sd, est + 2*sd)
conf
```
+Our 95% confidence interval is `r round(conf)`, meaning that if we repeated our test, the mean profit would lie somewhere between this range 95% of the time.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->
In conclusion, by repeating Brownlow's 1137 wagers 100 times, we estimated an average profit of $`r round(mean(ansarray))`. It is important to note that the number of students in the class, as well as the amount Brownlow wagered, influenced the earnings.
